sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-12-09 doc/paper.Rmd
Switch to miller2019

How does one choose among the related packages mentioned in this paper to fit SPDE-based geostatistical GLMMs?
Assuming a given package can fit the model of interest (Table 1), we suggest the primary difference is the user interface.
We think users familiar with `stats::glm()`, lme4, or glmmTMB will find sdmTMB most approachable.
Users familiar with INLA will find inlabru approachable.
Users already familiar with mgcv can adapt mgcv to fit similar models with custom code [e.g., @camp2020] and INLA/inlabru and mgcv are also general purpose modelling packages.
VAST is the sole option for fitting some multivariate models;
alternatively, because VAST focuses on multivariate delta models and fisheries applications, users fitting "simple" univariate spatial/spatiotemoral GLMMs may find sdmTMB more straightforward to use.
Users looking for calculation with uncertainty of derived variables such as area-weighted population indexes may favour sdmTMB or VAST (although such quantities can be post hoc derived with other packages).
Speed wise, sdmTMB (and VAST) may be fastest in some cases (e.g., random effect normalization) or in situations up to mid-resolution meshes (~500 knots), which in practice can cover fairly complex spatial processes on large datasets (e.g., REFs).
INLA/inlabru, or spaMM for spatial models, scale the best with very high resolution meshes.

>>>>

How does one choose among the related packages mentioned in this paper to fit SPDE-based geostatistical GLMMs?
Assuming a given package can fit the model of interest (Table 1), we suggest the primary difference is the user interface.
We think users familiar with `stats::glm()`, lme4, or glmmTMB will find sdmTMB most approachable.
Users familiar with INLA will find inlabru approachable.
Users already familiar with mgcv can adapt mgcv to fit similar models with custom code [@miller2019] and INLA/inlabru and mgcv are also general purpose modelling packages.
VAST is the sole option for fitting some multivariate models;
alternatively, because VAST focuses on multivariate delta models and fisheries applications, users fitting "simple" univariate spatial/spatiotemoral GLMMs may find sdmTMB more straightforward to use.
Users looking for calculation with uncertainty of derived variables such as area-weighted population indexes may favour sdmTMB or VAST (although such quantities can be post hoc derived with other packages).
Speed wise, sdmTMB (and VAST) may be fastest in some cases (e.g., random effect normalization) or in situations up to mid-resolution meshes (~500 knots), which in practice can cover fairly complex spatial processes on large datasets (e.g., REFs).
INLA/inlabru, or spaMM for spatial models, scale the best with very high resolution meshes.
